---
title: "Project 2 -- Predictive Models and Automation"
author: "Sandra Aziz"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project 2
For this project, I created the github repo page and added my partner as a collaborator so we could both push updates for the project. I also read in the data set required and did some summaries and analyses to have an idea of what the data we are dealing with looks like. Then, I wrote short introductions for the linear regression models and the random forests model, then did the comparison between all the models to figure out the best model with the lowest RMSE.  
Overall, I found this project to be less confusing/demanding than the first one. One problem that I ran into at the beginning was having trouble pulling updates from Github. I had to figure out how to navigate that since it was my first time working with a collaborator on the same project.  
What I learned the hard way was that the random forests model takes a very long time to run, especially with a large data set. A lot of the times I thought there was something wrong with the code because I never had a problem where rendering the code would be that slow. Lastly, even though I wasn't directly involved with the automation process, my partner added code throughout the project that made the process go more smoothly. That taught me that although I try to make my code very percise, more code is not always inefficient, sometimes it makes the rendering process less troublesome.  


[View my Github Pages](https://saziz12.github.io/ST558-Project2/) : This includes links to all the reports. 

[View my Github Repo](https://github.com/saziz12/ST558-Project2.git)  

```{r, eval=FALSE, echo=FALSE}
rmarkdown::render("~/Library/CloudStorage/OneDrive-NorthCarolinaStateUniversity/NCSU/Summer2023/ST 558/saziz12.github.io/_Rmd/2023-07-09-project02-blog.Rmd",
output_format = "github_document", 
output_dir = "_posts/",
output_options = list(html_preview=FALSE))
```
