---
title: "Blog Post 5"
author: "Sandra Aziz"
output: "github_document"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What now?

After this course on R, I think it's very useful for data science. I will most likely keep using R in the future since it has many ways to manipulate and analyze data. Another thing I like about R is its community of users. I love how everyone is sharing the new uses/ways they find and is helping others do the same.  

I am currently doing an internship where we use SAS to analyze clinical data, and after learning all about R in this course, I am interested to see how functions and uses translate between both languages. I found it interesting that as I was coding in SAS, the only thing I could think of was how much easier it would be to code in R instead.  

I am interested to learn more about clinical development and analysis, and since pharmaceutical companies are moving towards using more open source languages like R, I'm exciting to see what new things I can learn about it in the future!  


```{r render, echo=FALSE, eval=FALSE}
rmarkdown::render("~/Library/CloudStorage/OneDrive-NorthCarolinaStateUniversity/NCSU/Summer2023/ST 558/saziz12.github.io.git2/_Rmd/2023-07-27-blog-post-5.Rmd",
output_format = "github_document", 
output_dir = "_posts/",
output_options = list(html_preview=FALSE))
```